---
title: "Developmental change in prefrontal cortex recruitment supports the emergence of value-guided memory"
author: "Kate Nussenbaum"
date: "1/26/21"
output:
  html_document:
    df_print: paged
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
---
<style type="text/css">
h1.title {
font-size: 38px;
}
h1 { /* Header 1 */
font-size: 28px;
}
h2 { /* Header 2 */
font-size: 22px;
}
h3 { /* Header 3 */
font-size: 18px;
}

</style>
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = T)
knitr::opts_chunk$set(fig.path = "images/")
knitr::opts_chunk$set(fig.width=7, fig.height = 4.5, dpi = 300)
```

```{r load helper functions and libraries}
library(magrittr)
library(afex)
library(glue)
library(readxl)
library(pander)
library(Rmisc)
library(pander)
library(mediation)
source("scripts/helperFunctions.R") #Note: Currently loads tidyverse, plotting theme, age groups, scale_this function, and se function
library(sjPlot)

#deal with conflicting functions
select <- dplyr::select
rename <- dplyr::rename
mutate <- dplyr::mutate
filter <- dplyr::filter
```


```{r import data}
#set data folder
dataFolder <- "behav_data"

#identify relevant data files
freqfiles = list.files(dataFolder, pattern = "freqTask")
PAfiles = list.files(dataFolder, pattern = "PA")
memFiles = list.files(dataFolder, pattern = "a_mri")
freqReports = list.files(dataFolder, pattern = "freqReports")

#frequency data
freqData <- freqfiles %>%
  #read in files and set variable types
  map( ~ read_tsv(
    file.path(dataFolder, .),
    col_names = T,
    col_types = cols(
      sub = col_double(),
      cbVersion = col_double(),
      trial = col_number(),
      freqCond = col_double(),
      freqITI = col_double(),
      freqTaskResp = col_double(),
      freqTaskRT = col_double(),
      freqTrialStart = col_double(),
      freqTrialEnd = col_double(),
      freqTrialITIStart = col_double(),
      freqTrialITIEnd = col_double(),
      taskVersion = col_character(),
      block = col_double()
    )
  )) %>%
  #remove extra column if it exists
  map(~ .x %>% select(-matches("X"))) %>%
  reduce(bind_rows) %>%
  group_by(sub, stim) %>%
  mutate(stimNum = 1, freqAppearanceCount = cumsum(stimNum)) %>%
  ungroup() %>%
  dplyr::select(-c(stimNum)) %>%
  filter(trial > 0 & trial < 73)


#memory data
memData <- memFiles %>%
  map( ~ read_tsv(
    file.path(dataFolder, .),
    col_names = T,
    col_types = cols(
      sub = col_double(),
      trial = col_double(),
      stim = col_character(),
      freqCond = col_double(),
      truePair = col_character(),
      foilLowFreq = col_character(),
      foilHighFreq = col_character(),
      foilNovel = col_character(),
      truePairPos = col_double(),
      foilLowFreqPos = col_double(),
      foilHighFreqPos = col_double(),
      memResp = col_double(),
      memRT = col_double(),
      memTrialStart = col_double(),
      memTrialEnd = col_double(),
      memTrialITI = col_double(),
      memTrialITIStart = col_double(),
      memTrialITIEnd = col_double(),
      block = col_double()
    )
  )) %>%
  map(~ .x %>% select(-matches("X"))) %>%
  reduce(bind_rows) %>%
  mutate(memAcc = case_when(truePairPos == memResp ~ 1, truePairPos != memResp ~ 0)) %>%
  dplyr::filter(trial > 0 & trial < 25)


#frequency report data
freqReportData <- freqReports %>%
  map( ~ read_tsv(
    file.path(dataFolder, .),
    col_names = T,
    col_types = cols(
      sub = col_double(),
      trial = col_double(),
      stim = col_character(),
      freqReport = col_double(),
      freqReportRT = col_double(),
      freqReportTrialStart = col_double(),
      freqReportTrialEnd = col_double(),
      freqReportITI = col_double(),
      freqReportITITrialStart = col_double(),
      freqReportITITrialEnd = col_double(),
      block = col_double()
    )
  )) %>%
  map(~ .x %>% select(-contains("X"))) %>%
  reduce(bind_rows) %>%
  rename(freqReportTrial = trial) %>%
  filter(freqReportTrial > 0 & freqReportTrial < 25)

#combine memory data with frequency report data
memData <-
  full_join(memData, freqReportData, by = c("sub", "stim", "block")) %>%
  mutate_at(
    .vars = vars(stim, block, truePair, foilLowFreq, foilHighFreq, foilNovel),
    .funs = factor
  )

#read in subject list
subList <- read_tsv(glue("{dataFolder}/participant_info.txt"))

#add age groups
subList <- addAgeGroup(subList, age)

#merge with freq data memory data
freqData <- full_join(freqData, subList, by = c("sub")) %>%
  mutate_at(.vars = vars(sub), .funs = factor)

memData <- full_join(memData, subList, by = c("sub")) %>%
  mutate_at(.vars = vars(sub), .funs = factor)
```

# Participant stats
```{r sub stats}
subStatsPlot <-
  ggplot(subList, aes(x = age, fill = as.factor(gender))) +
  geom_histogram(boundary = 1,
                 binwidth = 1,
                 color = "white") +
  scale_fill_manual(
    values = c(color1, color3),
    name = "Sex",
    labels = c("Male", "Female")
  ) +
  ylab("Number of Participants") +
  xlab("Age") +
  kate.theme
subStatsPlot

#Mean and SD age for each age group
subStatsTable <- subList %>%
  group_by(ageGroup) %>%
  summarize(mean_age = mean(age),
            se_age = se(age),
            N = n())
pander(subStatsTable)

#Gender distribution in age group
gender_counts <- subList %>%
  group_by(ageGroup) %>%
  count(gender)
pander(gender_counts)

#race distribution
race_dist <- subList %>%
  count(race) %>%
  mutate(prop_race = n/90)
pander(race_dist)

#ethnicity distribution
hispanic_dist <- subList %>%
  count(hispanic) %>%
  mutate(prop_hisp = n/90)
pander(hispanic_dist)

#number of participants included in each part of the task
num_subs_behav1 <- subList %>%
  select(contains("1_behav")) %>%
  summarize(across(.cols = everything(), sum)) %>%
  mutate(data_type = "behav", block = 1) %>%
  rename_with(~ gsub("1_behav", "", .x, fixed = TRUE))

num_subs_behav2 <- subList %>%
  select(contains("2_behav")) %>%
  summarize(across(.cols = everything(), sum)) %>%
  mutate(data_type = "behav", block = 2) %>%
  rename_with(~ gsub("2_behav", "", .x, fixed = TRUE))

num_subs_neur1 <- subList %>%
  select(contains("1_neur")) %>%
  summarize(across(.cols = everything(), sum)) %>%
  mutate(data_type = "neur", block = 1) %>%
  rename_with(~ gsub("1_neur", "", .x, fixed = TRUE)) %>%
  mutate(fr  = NA)

num_subs_neur2 <- subList %>%
  select(contains("2_neur")) %>%
  summarize(across(.cols = everything(), sum)) %>%
  mutate(data_type = "neur", block = 2) %>%
  rename_with(~ gsub("2_neur", "", .x, fixed = TRUE)) %>%
  mutate(fr = NA)

#join
num_subs <- rbind(num_subs_behav1, num_subs_behav2, num_subs_neur1, num_subs_neur2) %>% relocate(data_type, block) %>%
  arrange(block)
pander(num_subs)

```

## Relation between age and IQ

### Should quadratic age be included in the model?
```{r age iq relation quadratic test}
subList$age_scaled <- scale_this(subList$age)
subList$age_squared_scaled <- scale_this((subList$age)^2)

age.IQ <- lm(IQ ~ age_scaled, data = subList)
age_sq.IQ <- lm(IQ ~ age_scaled + age_squared_scaled, data = subList)
anova(age.IQ, age_sq.IQ) #model with just age fits better
```
No, including quadratic age does not improve model fit.

### Is there a relation between age and IQ?
```{r age iq relation}
summary(age.IQ)

#plot relation
age.iq.plot <- ggplot(subList, aes(x = age, y = IQ)) +
  geom_point(color = color1) +
  geom_smooth(method = "lm",
              color = color3,
              fill = color3) +
  kate.theme
age.iq.plot 
```

There is a relation between age and IQ in the dataset. We will include IQ as an interacting fixed effect in all subsequent analyses to control for it.


# Frequency-learning
## Plot: Response accuracy by age group and appearance count
```{r frequency task accuracy}
#compute accuracy
freqData %<>% mutate(freqAcc = case_when(freqAppearanceCount == 1 & freqTaskResp == 1 ~ 1,
                                         freqAppearanceCount > 1 & freqTaskResp == 2 ~ 1,
                                         freqAppearanceCount == 1 & freqTaskResp == 2 ~ 0,
                                         freqAppearanceCount > 1 & freqTaskResp == 1 ~ 0),
                     freqTrialType = case_when(freqAppearanceCount == 1 ~ "new",
                                               freqAppearanceCount > 1 ~ "old")) %>%
  filter(is.na(freqAcc) == F) %>%
  filter(freqTaskRT > .20)

#compute mean response accuracy for old and new items per age group
freqTaskAgeGroupMeans <- summarySE(freqData, "freqAcc", c("ageGroup", "freqTrialType"))
pander(freqTaskAgeGroupMeans)

#compute mean response accuracy for old and new items
freqTrialTypeMeans <- summarySE(freqData, "freqAcc", c("freqTrialType"))
pander(freqTrialTypeMeans)

#compute mean response accuracy for each appearance count and age group
freqTaskAccMeans <- summarySE(freqData, "freqAcc", c("ageGroup", "freqAppearanceCount"))

#plot
freqAccPlot <-ggplot(freqTaskAccMeans, aes(x = freqAppearanceCount, y = freqAcc, color = ageGroup)) +
  geom_line(stat = "identity", size = 1) +
  geom_errorbar(aes(ymin = freqAcc - se, ymax = freqAcc + se), width = .1) +
  scale_color_manual(values = c(color1, color2, color3), name = "Age Group") +
  ylab("Frequency Response Accuracy") +
  xlab("Appearance Count") +
  kate.theme
freqAccPlot
```

## Model: Frequency learning response accuracy: new items
```{r response accuracy mixed model new}
freqDataNewItems <- freqData %>%
  filter(freqTrialType == "new") 
freqDataNewItems$ageScaled <- scale_this(freqDataNewItems$age)
freqDataNewItems$ageSquaredScaled <- scale_this(freqDataNewItems$age^2)
freqDataNewItems$IQScaled <- scale_this(freqDataNewItems$IQ)

freq.newItems.model <- mixed(freqAcc ~ ageScaled * IQScaled + (1|sub), 
                             data = freqDataNewItems, family = binomial, method = "LRT", 
                             control = glmerControl(optCtrl=list(maxfun=1e6)), 
                             expand_re = T, 
                             return = "merMod")

freq.newItems.model.2 <- mixed(freqAcc ~ (ageScaled + ageSquaredScaled) * IQScaled + (1|sub), 
                               data = freqDataNewItems, family = binomial, method = "LRT", 
                               control = glmerControl(optCtrl=list(maxfun=1e6)), 
                               expand_re = T, 
                               return = "merMod")

#compare models
anova(freq.newItems.model, freq.newItems.model.2) #model with just age fits better

#print stats of best-fitting model
freq.newItems.model.stats <- mixed(freqAcc ~ ageScaled * IQScaled + (1|sub), 
                                   data = freqDataNewItems, family = binomial, method = "LRT", 
                                   control = glmerControl(optCtrl=list(maxfun=1e6)), 
                                   expand_re = T)
freq.newItems.model.stats
# main effect of age
# main effect of IQ

tab_model(freq.newItems.model.stats)
```

## Model: Frequency learning response accuracy - repeated items
```{r response accuracy mixed model old}
freqDataOldItems <- freqData %>%
  filter(freqAppearanceCount > 1)
freqDataOldItems$ageScaled <- scale_this(freqDataOldItems$age)
freqDataOldItems$ageSquaredScaled <- scale_this(freqDataOldItems$age^2)
freqDataOldItems$IQScaled <- scale_this(freqDataOldItems$IQ)
freqDataOldItems$appearanceCountScaled <- scale_this(freqDataOldItems$freqAppearanceCount)

freq.oldItems.model <- mixed(freqAcc ~ appearanceCountScaled * ageScaled * IQScaled + (appearanceCountScaled|sub), 
                             data = freqDataOldItems, family = binomial, method = "LRT", 
                             control = glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"), 
                             expand_re = T, 
                             return = "merMod")

freq.oldItems.model.2 <- mixed(freqAcc ~ appearanceCountScaled * (ageScaled + ageSquaredScaled) * IQScaled + (appearanceCountScaled|sub), 
                               data = freqDataOldItems, family = binomial, method = "LRT", 
                               control = glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"), 
                               expand_re = T,
                               return = "merMod")

#compare models
anova(freq.oldItems.model, freq.oldItems.model.2) #model with just age fits better

#display stats for best fitting model
freq.oldItems.model.stats <- mixed(freqAcc ~ appearanceCountScaled * ageScaled * IQScaled + (appearanceCountScaled|sub), 
                             data = freqDataOldItems, family = binomial, method = "LRT", 
                             control = glmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"), 
                             expand_re = T)

freq.oldItems.model.stats
# main effect of age
# main effect of IQ
# main effect of appearance count
# age x appearance count interaction
tab_model(freq.oldItems.model.stats)
```

## Plot: Frequency learning reaction times by appearance count
```{r frequency task RTs plot}
#include accurate trials only
freqRTData <- freqData %>% 
  filter(freqAcc == 1) %>%
  filter(freqTaskRT > .2)

#compute mean RT for each age group and appearance count
freqTaskRTMeans <- summarySE(freqRTData, "freqTaskRT", c("freqAppearanceCount", "ageGroup"))

#plot
freqRTPlot <-ggplot(freqTaskRTMeans, aes(x = freqAppearanceCount, y = freqTaskRT, color = ageGroup, group = ageGroup)) +
  geom_line() +
  geom_errorbar(aes(ymin = freqTaskRT - se, ymax = freqTaskRT + se), width = .1) +
  scale_color_manual(values = c(color1, color2, color3), name = "Age Group") +
  ylab("Frequency Response RT") +
  xlab("Appearance Count") +
  kate.theme
freqRTPlot

#plot with continuous age
freqTaskRTSubMeans <- summarySE(freqRTData, "freqTaskRT", c("freqAppearanceCount", "age"))

freqRTAgePlot <- ggplot(freqTaskRTSubMeans, aes(x = age, y = freqTaskRT, color = factor(freqAppearanceCount), fill = factor(freqAppearanceCount), group = freqAppearanceCount)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = y ~ poly(x, 2)) +
  scale_color_brewer(name = "Item Repetition") +
  scale_fill_brewer(name = "Item Repetition") +
  ylab("Frequency-learning RT") +
  xlab("Age") +
  kate.theme
freqRTAgePlot
```

## Model: Frequency learning reaction times - new items
```{r freq RT model new}
freqRTDataNewItems <- freqRTData %>%
  filter(freqAppearanceCount == 1)

freqRTDataNewItems$ageScaled <- scale_this(freqRTDataNewItems$age)
freqRTDataNewItems$ageSquaredScaled <- scale_this(freqRTDataNewItems$age^2)
freqRTDataNewItems$IQScaled <- scale_this(freqRTDataNewItems$IQ)

freq.newItems.RT <- mixed(freqTaskRT ~  ageScaled * IQScaled + (1|sub), 
                          data = freqRTDataNewItems, method = "S", 
                          control = lmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"), 
                          expand_re = T, return = "merMod")

freq.newItems.RT.2 <- mixed(freqTaskRT ~  (ageScaled + ageSquaredScaled) * IQScaled + (1|sub), 
                            data = freqRTDataNewItems, method = "S", 
                            control = lmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"), 
                            expand_re = T, return = "merMod")

#compare models
anova(freq.newItems.RT, freq.newItems.RT.2) #model with age squared fits better

#display stats for best fitting model
freq.newItems.RT.2.stats <- mixed(freqTaskRT ~  (ageScaled + ageSquaredScaled) * IQScaled + (1|sub), 
                          data = freqRTDataNewItems, method = "S", 
                          control = lmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"), 
                          expand_re = T)
freq.newItems.RT.2.stats
#main effect of age
#main effect of quadratic age
# age x IQ interaction
# quadratic age x IQ interaction

tab_model(freq.newItems.RT.2.stats)
```

## Model: Frequency learning reaction times - repeated items
```{r freq RT model old}
freqRTDataOldItems <- freqRTData %>%
  filter(freqAppearanceCount > 1)

freqRTDataOldItems$ageScaled <- scale_this(freqRTDataOldItems$age)
freqRTDataOldItems$ageSquaredScaled <- scale_this(freqRTDataOldItems$age^2)
freqRTDataOldItems$IQScaled <- scale_this(freqRTDataOldItems$IQ)
freqRTDataOldItems$appearanceCountScaled <- scale_this(freqRTDataOldItems$freqAppearanceCount)

freq.oldItems.RT.model <- mixed(freqTaskRT ~  ageScaled * IQScaled * appearanceCountScaled + (appearanceCountScaled|sub), 
                          data = freqRTDataOldItems, method = "S", 
                          control = lmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"), 
                          expand_re = T, 
                          return = "merMod")

freq.oldItems.RT.model.2 <- mixed(freqTaskRT ~  (ageScaled + ageSquaredScaled) * IQScaled * appearanceCountScaled +  (appearanceCountScaled|sub), 
                            data = freqRTDataOldItems, method = "S", 
                            control = lmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"),
                            expand_re = T, 
                            return = "merMod")

#compare models
anova(freq.oldItems.RT.model, freq.oldItems.RT.model.2) #model with age^2 fits better

#display stats for best-fitting model
freq.oldItems.RT.2.stats <- mixed(freqTaskRT ~  (ageScaled + ageSquaredScaled) * IQScaled * appearanceCountScaled + (appearanceCountScaled|sub), 
                          data = freqRTDataOldItems, method = "S", 
                          control = lmerControl(optCtrl=list(maxfun=1e6), optimizer = "bobyqa"), 
                          expand_re = T)
freq.oldItems.RT.2.stats
# main effect of age
# main effect of IQ
# main effect of quadratic age
# main effect of appearance count
# quadratic age x IQ interaction

tab_model(freq.oldItems.RT.2.stats)
```


# Frequency reports
## Plot: Frequency report histograms
```{r frequency report histograms, fig.height = 4, fig.width = 8, dpi = 600}
#filter NA responses 
freqReports <- memData %>% 
  filter(freqReport > 0) %>%
  filter(freqReportRT > .20)

#compute mean frequency responses for each condition
freqReportMeans <- summarySE(freqReports, "freqReport", c("freqCond"))

#plot
freqRespHist <- ggplot(freqReports, aes(x = (freqReport),color = factor(freqCond),fill = factor(freqCond))) +
  stat_count(position = "identity", alpha = .5) +
  scale_fill_manual(values = c(color1, color3), name = "Frequency Condition") +
  scale_color_manual(values = c(color1, color3), name = "Frequency Condition") +
  scale_x_discrete(limits = factor(c(1:7))) +
  xlab("Reported Frequency") +
  ylab("Number of Responses") +
  facet_wrap( ~ ageGroup) +
  kate.theme
freqRespHist
```

## Plot: Frequency report error magnitudes
```{r freq rep error plot}
freqReports %<>% mutate(rep_error_mag = abs(freqReport - freqCond)) 

#compute mean freq_resp_error per subject
freq_rep_error <- summarySE(freqReports, "rep_error_mag", c("sub", "age", "freqCond"))

#plot
freq_resp_error_plot <- ggplot(freq_rep_error, aes(x = age, y = rep_error_mag, color = as.factor(freqCond))) +
  geom_point(alpha = .7) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), aes(fill = as.factor(freqCond))) + 
  scale_color_manual(values = c(color1, color3), name = "Frequency Condition") +
  scale_fill_manual(values = c(color1, color3), name = "Frequency Condition") +
  ylab("Mean Report Error Magnitude") +
  xlab("Age") +
  kate.theme
freq_resp_error_plot
```

## Table: Frequency report error magnitude descriptive stats
```{r freq rep error descriptive stats}
#compute mean freq_resp_error per age group
freq_rep_error_stats <- summarySE(freqReports, "rep_error_mag", c("ageGroup"))

#display
pander(freq_rep_error_stats)
```

## Model: Frequency report error magnitudes by age and frequency condition
```{r freq rep error magnitude model}
freqReports$ageScaled <- scale_this(freqReports$age)
freqReports$ageSquaredScaled <- scale_this(freqReports$age^2)
freqReports$IQScaled <- scale_this(freqReports$IQ)
freqReports$freqCond <- as.factor(freqReports$freqCond)

freqRep.model <- mixed(rep_error_mag ~ ageScaled * IQScaled *freqCond + (freqCond|sub),
                 data = freqReports, method = "S", 
                 control = lmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"), 
                 expand_re = T,
                 return = "merMod")

freqRep.2.model <- mixed(rep_error_mag ~ (ageScaled +ageSquaredScaled)* IQScaled *freqCond + (freqCond|sub),
                 data = freqReports, method = "S", 
                 control = lmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"), 
                 expand_re = T,
                 return = "merMod")

#compare models
anova(freqRep.model, freqRep.2.model) #model with age squared fits better

#display stats from best-fitting model
freqRep.2.stats <- mixed(rep_error_mag ~ (ageScaled + ageSquaredScaled)* IQScaled *freqCond + (freqCond|sub),
                 data = freqReports, method = "S", 
                 control = lmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"), 
                 expand_re = T)
freqRep.2.stats
# main effect of age
# main effect of quadratic age
# main effect of IQ

tab_model(freqRep.2.stats)
```


# Associative memory
## Plot: Memory performance by frequency condition: Individual subject data
```{r memory accuracy individual subjects plot}
#save unfiltered memory data
memData_unfiltered <- memData

#filter out inaccurate trials
memData <- memData %>%
  filter(is.na(memAcc) == F) %>%
  filter(memRT > .20)

#compute memory accuracy by frequency condition and age group
mem.freqCond <- summarySE(memData, "memAcc", c("freqCond", "ageGroup"))

#compute memory accuracy by frequency condition per subject
mem.freqCond.sub <- summarySE(memData, "memAcc", c("freqCond", "ageGroup", "sub", "age"))

# plot memory test accuracy as a function of frequency condition
memAccSubPlot <- ggplot(mem.freqCond, aes(x = factor(freqCond), y = memAcc, color = ageGroup)) +
  scale_color_manual(values = c(color1, color2, color3), name = "Age Group") +
  geom_point(data = mem.freqCond.sub, aes(x = factor(freqCond), y = memAcc, group = sub), alpha = .5) +
  geom_point(data = mem.freqCond, aes(x = factor(freqCond), y = memAcc, group = ageGroup), size = 2.5) +
  geom_line(data = mem.freqCond.sub, aes(group = sub, color = ageGroup), alpha = .5) +
  geom_line(data = mem.freqCond, aes(x = factor(freqCond), y = memAcc, group = ageGroup), size = 2.5) +
  coord_cartesian(ylim = c(0, 1)) +
  xlab("Frequency Condition") +
  ylab ("Memory Accuracy") +
  facet_wrap( ~ ageGroup) +
  kate.theme
memAccSubPlot
```

```{r mem sub stats for MRI}
#save memory stats to use for MRI analyses
memSubStats <- memData %>% 
  group_by(sub, age, freqCond) %>%
  dplyr::summarize(mean_mem = mean(memAcc, na.rm = T)) %>%
  spread(freqCond, mean_mem) %>%
  ungroup() %>%
  mutate(mem_diff = `5` - `1`) %>%
  dplyr::rename(high_acc = `5`, low_acc = `1`)

sub_stats_for_MRI <- memSubStats %>%
  select(sub, age, mem_diff) %>%
  mutate(age_demean = age - mean(memSubStats$age),
         mem_diff_demean = mem_diff - mean(memSubStats$mem_diff)) %>%
  select(sub, age, mem_diff, age_demean, mem_diff_demean)

#save as .txt
#write.table(sub_stats_for_MRI, file = "sub_mem_stats.txt", sep = "\t",
#          row.names = F)
```


## Plot: Memory performance by frequency condition
```{r memory accuracy continuous age plot}
# plot memory test accuracy as a function of continuous age
memAccPlot <- ggplot(mem.freqCond.sub, aes(x = age, y = memAcc, color = as.factor(freqCond))) +
  
  geom_point() +
  geom_smooth(formula = y ~ poly(x,2), method = lm, aes(fill = as.factor(freqCond))) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_color_manual(values = c(color1, color3), name = "Frequency Condition") +
  scale_fill_manual(values = c(color1, color3), name = "Frequency Condition") +
  xlab("Age") +
  ylab ("Memory Accuracy") +
  kate.theme
memAccPlot
```


## Model: Memory performance by frequency condition
```{r memory accuracy model}
memData$freqCond <- as.factor(memData$freqCond)
memData$ageScaled <- scale_this(memData$age)
memData$ageSquaredScaled <- scale_this(memData$age^2)
memData$IQScaled <- scale_this(memData$IQ)

mem.model <- mixed(memAcc ~ freqCond * ageScaled * IQScaled + (freqCond|sub), 
                   family = "binomial", method = "LRT", 
                   data = memData, 
                   control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), 
                   expand_re = T,
                   return = "merMod")

mem.model.2 <- mixed(memAcc ~ freqCond * IQScaled * (ageScaled + ageSquaredScaled) + (freqCond|sub), 
                     family = "binomial", method = "LRT", 
                     data = memData, 
                     control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)),
                     return = "merMod")

#compare models
anova(mem.model, mem.model.2) # model w/ age^2 fits better

#display stats of best-fitting model
mem.2.stats <- mixed(memAcc ~ freqCond * IQScaled * (ageScaled + ageSquaredScaled) + (freqCond|sub), 
                     family = "binomial", method = "LRT", 
                     data = memData, 
                     control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
mem.2.stats
# main effect of age
# main effect of quadratic age
# main effect of IQ
# main effect of frequency condition
# age x frequency condition interaction
# quadratic age x frequency condition interaction

tab_model(mem.2.stats)
```


## Plot: Memory performance by reported frequency
```{r memory accuracy by reported frequency plot, fig.height = 3, fig.width = 8}
#compute memory accuracy by reported frequency
mem.freqReportData <- memData %>% 
  filter(freqReport > 0)

mem.freqReport <- summarySE(mem.freqReportData, "memAcc", c("freqReport", "ageGroup"))

#create bar plot
membyFreqReportBarPlot <- ggplot(mem.freqReport, aes(x = as.factor(freqReport), y = memAcc, alpha = N)) +
  geom_bar(stat = "identity", position = position_dodge(.9), fill = color3, color = color3) +
  geom_errorbar(aes(ymin = memAcc - se, ymax = memAcc + se), position = position_dodge(.9), width = .1) +
  facet_wrap(~ageGroup) +
  scale_alpha(breaks = c(50, 100, 150, 200, 250, 300)) + 
  ylab("Memory Accuracy") +
  xlab("Frequency Report") +
  kate.theme
membyFreqReportBarPlot

```


## Model: Memory performance by reported frequency
```{r freq mem model}
memFreqData <- memData %>%
  filter(freqReport > 0)

memFreqData$freqReportScaled <- scale_this(memFreqData$freqReport)
memFreqData$ageScaled <- scale_this(memFreqData$age)
memFreqData$ageSquaredScaled <- scale_this(memFreqData$age^2)
memFreqData$IQScaled <- scale_this(memFreqData$IQ)

mem.freq.model <- mixed(memAcc ~ freqReportScaled * ageScaled * IQScaled  + (freqReportScaled|sub), 
                        family = "binomial", method = "LRT", 
                        data = memFreqData, 
                        control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), 
                        expand_re = T,
                        return = "merMod")

mem.freq.model.2 <- mixed(memAcc ~ freqReportScaled * (ageScaled + ageSquaredScaled) * IQScaled  + (freqReportScaled|sub), 
                          family = "binomial", method = "LRT",
                          data = memFreqData, 
                          control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), 
                          expand_re = T,
                          return = "merMod")

#compare models
anova(mem.freq.model, mem.freq.model.2) #model w/ quadratic age fits better

#display stats of best-fitting model
mem.freq.2.stats <- mixed(memAcc ~ freqReportScaled * (ageScaled + ageSquaredScaled) *IQScaled  + (freqReportScaled|sub), 
                          family = "binomial", method = "LRT",
                          data = memFreqData, 
                          control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), 
                          expand_re = T)
mem.freq.2.stats
# main effect of age
# main effect of quadratic age
# main effect of IQ
# main effect of frequency report
# freq report x age
# freq report x quadratic age

tab_model(mem.freq.2.stats)
```

## Model: Comparison of frequency report vs. frequency condition as predictors
```{r freq reports vs. freq cond}
#determine whether frequency report model (mem.freq.model.2) or frequency condition model fits better

mem.freq.cond.model <- mixed(memAcc ~ freqCond * (ageScaled + ageSquaredScaled) *IQScaled + (freqCond|sub), 
                             family = "binomial", method = "LRT", 
                             data = memFreqData, 
                             control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), 
                             expand_re = T)

#compare models
anova(mem.freq.cond.model, mem.freq.model.2)

#frequency report model fits better
```


# Brain-behavior relations
```{r mem neural data processing}
#Read in files with neural estimates

#Cope 1 (Encoding > Baseline): PFC Sphere
mean_pfc <- read_csv("neural_data/encoding_vs_baseline_pfc.txt", col_names = "mean_pfc")

#Cope 5 (High Freq > Low Freq): PFC Sphere
freq_diff_pfc <- read_csv("neural_data/encoding_high_vs_low_pfc.txt", col_names = "freq_pfc")

# Cope 5 (High Freq > Low Freq): Caudate Sphere
freq_diff_caudate <- read_csv("neural_data/encoding_high_vs_low_caudate.txt", col_names = "freq_caudate")

# Subject order
sub_order <- read_csv("neural_data/sublist_ordered.txt", col_names = "sub") 

encoding_estimates <- bind_cols(sub_order, mean_pfc, freq_diff_pfc, freq_diff_caudate) 
encoding_estimates$sub <- as.factor(encoding_estimates$sub)

#combine w/ memory estimates
mem_means <- full_join(memSubStats, encoding_estimates, by = c("sub"))

#add IQ
IQList <- subList %>%
  select(sub, IQ)
IQList$sub <- as.factor(IQList$sub)

mem_means <- full_join(mem_means, IQList, by = c("sub"))
```


## Overall PFC activity during encoding

### Model: Overall PFC activity by age
```{r mean PFC age model}
#How does overall PFC activity at encoding relate to age? 

#scale variables
mem_means$ageScaled <- scale_this(mem_means$age)
mem_means$IQScaled <- scale_this(mem_means$IQ)
mem_means$ageSquaredScaled <- scale_this(mem_means$age^2)
mem_means$mean_pfc_scaled <- scale_this(mem_means$mean_pfc)

#Is overall PFC activity predicted by age and quadratic age?
mean_pfc_model.age <- lm(mean_pfc_scaled  ~ ageScaled * IQScaled, data = mem_means)
mean_pfc_model.age.2 <- lm(mean_pfc_scaled  ~ (ageScaled + ageSquaredScaled) * IQScaled, data = mem_means)

#compare models
anova(mean_pfc_model.age.2, mean_pfc_model.age) #model with just age fits better

#display best-fitting model stats
summary(mean_pfc_model.age)
#There is a main effect of linear age on overall PFC activity at encoding.
```

PFC activity during encoding increases with age.

### Model: Memory difference scores by overall PFC activity
```{r mean PFC mem_diff model}
#How does overall PFC activity at encoding relate to memory difference scores?

#scale variables
mem_means$mean_pfc_scaled <- scale_this(mem_means$mean_pfc)

memDiff_mean_pfc <- lm(mem_diff ~ mean_pfc_scaled * ageScaled * IQScaled, data = mem_means)
memDiff_mean_pfc.2 <- lm(mem_diff ~ mean_pfc_scaled * (ageScaled + ageSquaredScaled) * IQScaled, data = mem_means)

#compare models
anova(memDiff_mean_pfc, memDiff_mean_pfc.2) #model with quadratic age fits better

#display stats from best-fitting model
summary(memDiff_mean_pfc.2)
# main effect of age
# main effect of quadratic age
# no effect of PFC activity
```

Overall PFC activity at encoding does not relate to memory difference scores.


## PFC modulation (high vs. low frequency) during encoding

### Model: PFC modulation by age
```{r freq PFC age}
#scale freq_pfc
mem_means$freq_pfc_scaled <- scale_this(mem_means$freq_pfc)

#Is there a relation between age and PFC modulation?
freq_pfc_model.age <- lm(freq_pfc_scaled ~ (ageScaled) * IQScaled, data = mem_means)
freq_pfc_model.age.2 <- lm(freq_pfc_scaled ~ (ageScaled + ageSquaredScaled) * IQScaled, data = mem_means)

#compare models
anova(freq_pfc_model.age, freq_pfc_model.age.2) #model with age^2 fits better

#display stats from best-fitting model
summary(freq_pfc_model.age.2)
#main effect of age
#main effect of quadratic age
#main effect of IQ
```

PFC activity increases non-linearly with age.

### Plot: PFC modulation by age
```{r PFC age plot}
pfc_age_plot <- ggplot(mem_means, aes(x = age, y = freq_pfc)) +
  geom_point(color = color3) + 
  geom_smooth(method = "lm", formula = y ~ poly(x,2), color = color1, fill = color1) +
  xlab("Age") +
  ylab("PFC Modulation") +
  kate.theme
pfc_age_plot
```


### Mediation: Does PFC modulation mediate the relation between age and memory difference scores?
```{r mem pfc mediation}
# Does PFC modulation mediate the relation between age and memory difference scores?

# DV: Memory Difference Scores
# IV: Age
# Mediator: PFC Activity
# Control variables: Age^2, IQ

#scale memory difference scores
mem_means$mem_diff_scaled <- scale_this(mem_means$mem_diff)

# Step 1: The total effect - is there a relation between age and memory difference scores? DV ~ IV
fit.totaleffect <- lm(mem_diff_scaled ~ (ageScaled + ageSquaredScaled) + IQScaled, mem_means)
summary(fit.totaleffect)

# Answer: Yes.

# Step 2: The effect of the IV on the mediator - is there a relation between age and pfc modulation?
# Mediator ~ IV
fit.mediator <- lm(freq_pfc_scaled ~ (ageScaled + ageSquaredScaled) + IQScaled, mem_means)
summary(fit.mediator)

# Answer: Yes

# Step 3: The effect of the mediator on the DV while controlling for the IV
# Is there a relation between pfc activity and memory difference scores when controlling for age?
# DV ~ IV + Mediator
fit.dv <- lm(mem_diff_scaled ~ (ageScaled + ageSquaredScaled) + IQScaled + freq_pfc_scaled, mem_means)
summary(fit.dv)

#Yes, evidence for a partial mediation

# Step 4: Causal mediation analysis - treat = IV, mediator = mediator
med.out = mediate(fit.mediator, fit.dv, treat='ageScaled', mediator='freq_pfc_scaled', boot=T)

#examine results
mediation_results <- summary(med.out)
mediation_results

#Overall this suggests that there is a mediation.
```

Overall, this suggests that PFC activity mediates the relation between age and memory difference scores, while controlling for IQ and quadratic age.


### Mediation: Does the mediation hold without controlling for IQ and quadratic age?
```{r mem pfc mediation no covariates}
# Does PFC modulation mediate the relation between age and memory difference scores?

# DV: Memory Difference Scores
# IV: Age
# Mediator: PFC Activity

# Step 1: The total effect - is there a relation between age and memory difference scores? DV ~ IV
fit.totaleffect <- lm(mem_diff_scaled ~ ageScaled, mem_means)
summary(fit.totaleffect)

# Answer: Yes.

# Step 2: The effect of the IV on the mediator - is there a relation between age and pfc modulation?
# Mediator ~ IV
fit.mediator <- lm(freq_pfc_scaled ~ (ageScaled), mem_means)
summary(fit.mediator)

# Answer: marginal

# Step 3: The effect of the mediator on the DV while controlling for the IV
# Is there a relation between pfc activity and memory difference scores when controlling for age?
# DV ~ IV + Mediator
fit.dv <- lm(mem_diff_scaled ~ ageScaled + freq_pfc_scaled, mem_means)
summary(fit.dv)

#Yes.

# Step 4: Causal mediation analysis - treat = IV, mediator = mediator
med.out = mediate(fit.mediator, fit.dv, treat='ageScaled', mediator='freq_pfc_scaled', boot=T)

#examine results
mediation_results <- summary(med.out)
mediation_results

#Overall this suggests that there is a mediation.
```
Yes, even without controlling for IQ and quadratic age, PFC activity mediates the relation between age and memory difference scores.


### Mediation: Does age mediate the relation between PFC activity and memory difference scores?
```{r mem pfc mediation reverse}
# DV: Memory Difference Scores
# IV: PFC activity
# Mediator: Age

# Step 1: The total effect - is there a relation between memory difference scores and pfc activity? DV ~ IV
fit.totaleffect <- lm(mem_diff_scaled ~ freq_pfc_scaled, mem_means)
summary(fit.totaleffect)

# Answer: Yes.

# Step 2: The effect of the IV on the mediator - is there a relation between age and pfc modulation?
# Mediator ~ IV
fit.mediator <- lm(ageScaled ~ freq_pfc_scaled, mem_means)
summary(fit.mediator)

# Answer: Marginal.

# Step 3: The effect of the mediator on the DV while controlling for the IV
# Is there a relation between age and memory difference scores when controlling for pfc activity?
# DV ~ IV + Mediator
fit.dv <- lm(mem_diff_scaled ~ ageScaled + freq_pfc_scaled, mem_means)
summary(fit.dv)

#Answer: Yes.

# Step 4: Causal mediation analysis - treat = IV, mediator = mediator
med.out = mediate(fit.mediator, fit.dv, treat='freq_pfc_scaled', mediator='ageScaled', boot=T)


#examine results
mediation_results <- summary(med.out)
mediation_results

#Overall this suggests that there is NOT a mediation.
```

No, age does not significantly mediate the relation between PFC activity and memory difference scores.

## Caudate modulation (high vs. low frequency) during encoding

### Model: Caudate modulation by age
```{r freq caudate age}
mem_means$freq_caudate_scaled <- scale_this(mem_means$freq_caudate)

#Is there a relation between age and caudate modulation?
freq_caudate_model.age <- lm(freq_caudate_scaled ~ (ageScaled) * IQScaled, data = mem_means)
freq_caudate_model.age.2 <- lm(freq_caudate_scaled ~ (ageScaled + ageSquaredScaled) * IQScaled, data = mem_means)

#compare models
anova(freq_caudate_model.age, freq_caudate_model.age.2) #model with just age fits best

#display stats from best-fitting model
summary(freq_caudate_model.age)
# no effect of age
# no effect of IQ
# age x IQ interaction

summary(freq_caudate_model.age.2)
```
No.

### Model: Memory difference scores by caudate modulation
```{r freq caudate mem difference}
#How does PFC modulation at encoding relate to memory difference scores?
mem_means$freq_caudate_scaled <- scale_this(mem_means$freq_caudate)

#scale variables
memDiff_freq_caudate <- lm(mem_diff ~ freq_caudate_scaled * ageScaled * IQScaled, data = mem_means)
memDiff_freq_caudate.2 <- lm(mem_diff ~ freq_caudate_scaled * (ageScaled + ageSquaredScaled) * IQScaled, data = mem_means)

#compare models
anova(memDiff_freq_caudate, memDiff_freq_caudate.2) #model with quadratic age fits better

#display stats from best-fitting model
summary(memDiff_freq_caudate.2)
# main effect of age
# main effect of quadratic age
# no effect of caudate activity
```
No.

# Repetition suppression
```{r repetition suppression data processing}
# Read in neural data
RS_estimates <- read_csv("neural_data/RS_estimates.csv")

#Combine mem data with RS data
RS_estimates$sub <- as.factor(RS_estimates$sub)
RS_estimates$block <- as.factor(RS_estimates$block)

#combine RS data with memory data
temp <- full_join(memData_unfiltered, RS_estimates, by = c("sub", "stim", "block")) %>%
  filter(freqCond == 5) %>%
  select(sub, age, ageGroup, IQ, block, stim, memAcc, freqReport, phc1, phc5, decrease) %>%
  rename(phc_decrease = decrease)

RS_data_all <- temp

# Remove outliers from neural data 
phc_outlier_min <- mean(RS_data_all$phc_decrease, na.rm = T) - 3*sd(RS_data_all$phc_decrease, na.rm = T)
phc_outlier_max <- mean(RS_data_all$phc_decrease, na.rm = T) + 3*sd(RS_data_all$phc_decrease, na.rm = T)

phc_data <- RS_data_all %>%
  filter(phc_decrease > phc_outlier_min) %>%
  filter(phc_decrease < phc_outlier_max) %>%
  select(sub, age, ageGroup, IQ, block, stim, memAcc, freqReport, phc_decrease)

phc_num_outliers <- RS_data_all %>%
  filter(is.na(phc_decrease) == F) %>%
  nrow() - nrow(phc_data)
```

## Model: Repetition suppression and age
```{r RS and age}

#----- Model 1: Is there a relation between the decrease in phc activity and participant age? -----
# select data 
model1_data <- phc_data %>%
  select(sub, age, IQ, block, stim, phc_decrease) %>%
  drop_na() %>%
  mutate(age_scaled = scale_this(age),
         IQ_scaled = scale_this(IQ),
         phc_decrease_scaled = scale_this(phc_decrease),
         age_squared_scaled = scale_this(age^2),
         age_scaled_squared = age_scaled^2) %>%
  droplevels()


# run model
model.1.1 <- mixed(phc_decrease ~  IQ_scaled * (age_scaled) + 
                     (1|sub), 
                   data = model1_data, 
                   method = "S",
                   control = lmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"))

model.1.2 <- mixed(phc_decrease ~  IQ_scaled * (age_scaled + age_squared_scaled) + 
                   (1|sub), 
                 data = model1_data, 
                 method = "S",
                 control = lmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"))


anova(model.1.1, model.1.2) #model with age squared fits better

#display results
model.1.2
# Main effect of linear age
# Main effect of quadratic age

tab_model(model.1.2)
```

## Plot: Repetition suppression and age
```{r RS age plot}
#compute mean for each participant
RS_means <- model1_data %>%
  group_by(sub, age) %>%
  summarize(mean_RS = mean(phc_decrease, na.rm = T))

RS_age_plot <- ggplot(RS_means, aes(x = age, y = mean_RS)) +
  geom_point(color = color1) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), color = color3, fill = color3) +
  ylab("Mean Reptition Suppression") +
  xlab("Age") +
  kate.theme
RS_age_plot
```


## Model: Repetition suppression and frequency reports
```{r RS frequency reports}
#----- Model 2: Is there a relation between the decrease in phc activity and reports of item frequency? -----
# select data 
model2_data <- phc_data %>%
  select(sub, age, IQ, block, stim, phc_decrease, freqReport) %>%
  drop_na() %>%
  mutate(age_scaled = scale_this(age),
         IQ_scaled = scale_this(IQ),
         phc_decrease_scaled = scale_this(phc_decrease),
         age_squared_scaled = scale_this(age^2)) %>%
  droplevels()


# run model
model.2.1 <- mixed(freqReport ~ phc_decrease_scaled * IQ_scaled * age_scaled + 
                   (phc_decrease_scaled|sub), 
                 data = model2_data, 
                 method = "S",
                 control = lmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"), 
                 expand_re = T)

model.2.2 <- mixed(freqReport ~ phc_decrease_scaled * IQ_scaled * (age_scaled + age_squared_scaled) + 
                     (phc_decrease_scaled|sub), 
                   data = model2_data, 
                   method = "S",
                   control = lmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"), 
                   expand_re = T)

anova(model.2.1, model.2.2) #model with just age fits better

#display results
model.2.1
# No effects of phc decrease on frequency report

tab_model(model.2.1)
```

### Model: Repetition suppression and associative memory
```{r RS and memory}

#----- Model 3: Is there a relation between the decrease in phc activity and associative memory for each item? -----
# select data 
model3_data <- phc_data %>%
  select(sub, age, ageGroup, IQ, block, stim, phc_decrease, memAcc) %>%
  drop_na() %>%
  mutate(age_scaled = scale_this(age),
         IQ_scaled = scale_this(IQ),
         phc_decrease_scaled = scale_this(phc_decrease),
         age_squared_scaled = scale_this(age^2)) %>%
    droplevels()

# run model
model.3.1 <- mixed(memAcc ~ phc_decrease_scaled * IQ_scaled * age_scaled + 
                   (phc_decrease_scaled | sub), 
                 data = model3_data,
                 family = "binomial",
                 method = "LRT",
                 control = glmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"), 
                 expand_re = T)

model.3.2 <- mixed(memAcc ~ phc_decrease_scaled * IQ_scaled * (age_scaled + age_squared_scaled) + 
                   (phc_decrease_scaled | sub), 
                 data = model3_data,
                 family = "binomial",
                 method = "LRT",
                 control = glmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"), 
                 expand_re = T)

anova(model.3.1, model.3.2) #model with just age squared fits better

#display results
model.3.2
# Main effect of PHC decrease

tab_model(model.3.2)
```

## Plot: Memory accuracy by repetition suppression
```{r RS mem plot}

#bin phc_decrease into 7 bins
model3_data$phc_bins <- cut(model3_data$phc_decrease, breaks = c(-Inf, -150, 0, 150, 300, Inf), include.lowest = T)

#summarize
phc_mem_acc_means <- summarySE(model3_data, "memAcc", c("phc_bins", "ageGroup"))

#create bar plot
membyRSBarPlot <- ggplot(phc_mem_acc_means, aes(x = as.factor(phc_bins), y = memAcc, alpha = N)) +
  geom_bar(stat = "identity", position = position_dodge(.9), fill = color1, color = color1) +
  geom_errorbar(aes(ymin = memAcc - se, ymax = memAcc + se), position = position_dodge(.9), width = .1) +
  facet_wrap(~ageGroup) +
  scale_alpha(breaks = c(50, 100, 150, 200, 250, 300)) + 
  scale_x_discrete(labels = c("<-150", "-150-0", "0-150", "150-300", ">300")) +
  ylab("Memory Accuracy") +
  xlab("Repetition Suppression") +
  kate.theme +
  theme(axis.text.x = element_text(size = 7))
membyRSBarPlot
```

### Model: Memory by repetition suppression and frequency reports
```{r memory by RS and freq reports}

#----- Model 4: Do frequency reports and repetition suppression explain distinct sources of variance in memory? ----
model4_data <- full_join(model2_data, model3_data, by = c("sub", "age", "IQ", "block", "stim", "phc_decrease")) %>%
  select(sub, age, IQ, block, stim, phc_decrease, freqReport, memAcc) %>%
  drop_na() %>%
  mutate(age_scaled = scale_this(age),
         IQ_scaled = scale_this(IQ),
         phc_decrease_scaled = scale_this(phc_decrease),
         age_squared_scaled = scale_this(age^2),
         freq_report_scaled = scale_this(freqReport)) %>%
  droplevels()
                      
# run model
model.4.1 <- mixed(memAcc ~ age_scaled * IQ_scaled * phc_decrease_scaled * freq_report_scaled  + (phc_decrease_scaled * freq_report_scaled|sub), 
                 data = model4_data,
                 family = "binomial",
                 method = "LRT",
                 control = glmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"), 
                 expand_re = T)

model.4.2 <- mixed(memAcc ~ (age_scaled + age_squared_scaled) * IQ_scaled * phc_decrease_scaled * freq_report_scaled  + (phc_decrease_scaled * freq_report_scaled|sub), 
                 data = model4_data,
                 family = "binomial",
                 method = "LRT",
                 control = glmerControl(optCtrl = list(maxfun=1e6), optimizer = "bobyqa"), 
                 expand_re = T)

#compare model fit
anova(model.4.1, model.4.2) #model with age squared fits better

#display results
model.4.2

tab_model(model.4.2)
```